Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-02-17 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added a section on priors

%%%%%%%%%%%%%%%%%
\section{Results using LIGO-Virgo events}
\label{sec:results}
%%%%%%%%%%%%%%%%%

\subsection{Bayesian formalism}
If we assume that a GW signal observed in detector data $d$ is accurately described by our waveform model \pSEOB{}, we can infer the parameters of the model, $\bm{\lambda}$, given the hypotheis $\mathcal{H}$, using the Bayes theorem,
%
\begin{equation}
P(\bm{\lambda} \vert d, \mathcal{H}) =
\frac{P(\bm{\lambda} \vert \mathcal{H}) P(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
\label{eq:bayes}
\end{equation}
%
where $P(\bm{\lambda} \vert d, \mathcal{H})$ is the posterior probability distribution,
$P(\bm{\lambda} \vert \mathcal{H})$ the prior,
$P(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
$P(d \vert \mathcal{H})$ the evidence. The set of parameters, $\bm{\lambda}$, detailed in Sec.~\ref{sec:review_pSEOB}
include the set of beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$.
%
As discussed in Secs.~\ref{sec:review_theories} and \ref{sec:theory_specific_qnm}, there is a single coupling
constants in the cases of EdGB and dCS theories, but two in the cubic and
quartic EFTofGR. We also hold the other beyond-GR parameters, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$
fixed to theory-specific predictions. Hence, our set of beyond--GR parameters only includes the parameter $\{\ell \}$.
%

@@

\subsection{Event selection}

@@

\subsection{Einstein-dilaton-Gauss-Bonnet}
\label{sec:results_edgb}

\subsection{Dynamical Chern-Simons}
\label{sec:results_dcs}

@@

\subsection{Effective-field-theory of general relativity}
\label{sec:results_efts}

>>>>

%%%%%%%%%%%%%%%%%
\section{Results using LIGO-Virgo events}
\label{sec:results}
%%%%%%%%%%%%%%%%%
\subsection{Parameter Inference}

\subsubsection{Bayesian formalism}
If we assume that a GW signal observed in detector data $d$ is accurately described by our waveform model \pSEOB{}, we can infer the parameters of the model, $\bm{\lambda}$, given the hypotheis $\mathcal{H}$, using the Bayes theorem,
%
\begin{equation}
P(\bm{\lambda} \vert d, \mathcal{H}) =
\frac{P(\bm{\lambda} \vert \mathcal{H}) P(d \vert \bm{\lambda},\mathcal{H})}{P(d \vert \mathcal{H})}\,,
\label{eq:bayes}
\end{equation}
%
where $P(\bm{\lambda} \vert d, \mathcal{H})$ is the posterior probability distribution,
$P(\bm{\lambda} \vert \mathcal{H})$ the prior,
$P(d \vert \bm{\lambda},\mathcal{H})$ the likelihood, and
$P(d \vert \mathcal{H})$ the evidence. The set of parameters, $\bm{\lambda}$, detailed in Sec.~\ref{sec:review_pSEOB}
include the set of beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}, \delta \tau_k^{(j)}\}$.
%
As discussed in Secs.~\ref{sec:review_theories} and \ref{sec:theory_specific_qnm}, there is a single coupling
constants in the cases of EdGB and dCS theories, but two in the cubic and
quartic EFTofGR. We also hold the other beyond-GR parameters, $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$
fixed to theory-specific predictions. Hence, our set of beyond--GR parameters only includes the parameter $\{\ell \}$.
%

@@

\subsubsection{Priors}

The prior probability distribution functions on the GR parameters are assumed to be uniform over the component masses, $(m_1, m_2)$, isotropically distributed on a sphere in the sky for the source location with $p(d_L) \propto d_L^2$, and isotropic on the binary orientation, $p(\iota, \psi, \phi_0) \propto \text{sin} \iota$. For the spins $(\chi_1, \chi_2)$, we assume a prior uniform and isotropic in the spin magnitudes and restrict ourselves to the z-components~\footnote{This spin-prior choice can be specified in \texttt{LALInference} using the option \texttt{alignedspin-zprior}.} The prior on $t_0$ is uniform and its range is informed by our detection pipelines.

Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$, as already mentioned in the previous section, we would mostly hold $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$ to freely vary. For such cases, we assume a prior uniform between appropriate ranges on $\ell$.

\subsubsection{Event selection}

@@

\subsection{Results}

\subsubsection{Einstein-dilaton-Gauss-Bonnet}
\label{sec:results_edgb}

\subsubsection{Dynamical Chern-Simons}
\label{sec:results_dcs}

@@

\subsubsection{Effective-field-theory of general relativity}
\label{sec:results_efts}
